### 2024-09-20 cv/cv-body.tex
Add paper
cv

\begin{description}
\tightlist
\item[2021--23]
Research Scientist, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada
\item[2019--23]
Associate Editor, the Canadian Journal of Fisheries and Aquatic Sciences
\item[2020--23]
Adjunct Professor, Department of Mathematics, Simon Fraser University
\item[2017--20]
Program Head in Analytical Approaches and Spatial Stock Assessment,
Groundfish Section, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie University
\end{description}

@@

\begin{description}
\tightlist
\item[2024]
Thorson, J.T., \textbf{S.C. Anderson}, P. Goddard, C.N. Rooper.
tinyVAST: R package with an expressive interface to specify lagged and
simultaneous effects in multivariate spatio-temporal models. arXiv.
\url{https://doi.org/10.48550/arXiv.2401.10193}.
\item[2022]
\textbf{Anderson, S.C.}, E.J. Ward, P.A. English, L.A.K. Barnett, J.T.
Thorson. sdmTMB: an R package for fast, flexible, and user-friendly
generalized linear mixed effects models with spatial and spatiotemporal
random fields. bioRxiv 2022.03.24.485545.
\url{https://doi.org/10.1101/2022.03.24.485545}.
\item[2021]
\textbf{Anderson, S.C}, B.M. Connors, P.A. English, R.E. Forrest, R.
Haigh, K.R. Holt. Trends in Pacific Canadian groundfish stock status.
bioRxiv 2021.12.13.472502.
\url{https://doi.org/10.1101/2021.12.13.472502}.
\end{description}

@@

@@

K.L. Blake, D. Veríssimo, \textbf{S.C. Anderson}, A. Gleave. Do species
receive more attention when named after celebrities? Conservation

>>>>

\begin{description}
\tightlist
\item[2021--24]
Research Scientist, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada
\item[2019--24]
Associate Editor, the Canadian Journal of Fisheries and Aquatic Sciences
\item[2020--23]
Adjunct Professor, Department of Mathematics, Simon Fraser University
\item[2017--20]
Program Head in Analytical Approaches and Spatial Stock Assessment,
Groundfish Section, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie University
\end{description}

@@

\begin{description}
\tightlist
\item[2024]
Ward, E.J., \textbf{S.C. Anderson}, L.A.K. Barnett, P.A. English, H.M.
Berger, C.J.C. Commander, T.E Essington, C.J Harvey, M.E. Hunsicker, M.
Jacox, K.F Johnson, S. Large, O.R. Liu, K. Richerson, J.F. Samhouri,
S.A. Siedlecki, A.O. Shelton, K.A. Somers, and J.T. Watson. Win, lose,
or draw: evaluating dynamic thermal niches of northeast Pacific
groundfish. EarthArXiv Preprint. \url{https://doi.org/10.31223/X5J113}.
\item[2024]
Indivero, J., \textbf{S.C. Anderson}, L.A.K. Barnett, T.E. Essington,
and E.J. Ward. Estimating physiological mechanisms from monitoring data
reveals challenges and opportunities for forecasting distribution
shifts. Authorea Preprint.
\url{https://doi.org/10.22541/au.172446072.20202938/v1}.
\item[2024]
Thorson, J.T., \textbf{S.C. Anderson}, P. Goddard, C.N. Rooper.
tinyVAST: R package with an expressive interface to specify lagged and
simultaneous effects in multivariate spatio-temporal models. arXiv.
\url{https://doi.org/10.48550/arXiv.2401.10193}.
\item[2021]
\textbf{Anderson, S.C}, B.M. Connors, P.A. English, R.E. Forrest, R.
Haigh, K.R. Holt. Trends in Pacific Canadian groundfish stock status.
bioRxiv 2021.12.13.472502.
\url{https://doi.org/10.1101/2021.12.13.472502}.
\end{description}

@@

\textbf{Anderson, S.C.}, E.J. Ward, P.A. English, L.A.K. Barnett, and
J.T. Thorson. sdmTMB: an R package for fast, flexible, and user-friendly
generalized linear mixed effects models with spatial and spatiotemporal
random fields. In press at Journal of Statistical Software. Preprint:
bioRxiv 2022.03.24.485545.
\url{https://doi.org/10.1101/2022.03.24.485545}.
Freshwater, C., \textbf{S.C. Anderson}, and J. King. Model-based indices
of juvenile Pacific salmon abundance highlight species-specific seasonal
distributions and impacts of changes to survey design. Fisheries
Research. 277: 107063.
\url{https://doi.org/10.1016/j.fishres.2024.107063}.
Bass, A.L., Anderson, S.C., Bateman, A.W., Connors, B.M., Peña, M.A.,
Li, S., Kaukinen, K.H., Patterson, D.A., Hinch, S. G., and Miller, K.M.
2024. Intrinsic and extrinsic factors associated with the
spatio-temporal distribution of infectious agents in early marine
Chinook and coho salmon. Marine Ecology Progress Series. 736: 107--127.
\url{https://doi.org/10.3354/meps14581}.
Freshwater, C., \textbf{S.C. Anderson}, D.D. Huff, J.M. Smith, D.
Jackson, B. Hendriks, S.G. Hinch, S. Johnston, A.W. Trites, and J. King.
Chinook salmon depth distributions on the continental shelf are shaped
by interactions between location, season, and individual condition.
Movement Ecology. 12(1): 21.
\url{https://doi.org/10.1186/s40462-024-00464-y}.

@@

K.L. Blake, D. Veríssimo, \textbf{S.C. Anderson}, A. Gleave. Impact on
species' online attention when named after celebrities. Conservation
